```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(echo = TRUE, comment = "", out.width="90%",fig.asp=.56, fig.align = "center", message=FALSE)
```



## Setup
### Install and Attach
`installr` provides `require2`, this will install a package if it is missing and library it.  Unfortunately, `intall` is a package too, so you cannot use `require2` on it.
```{r, message = FALSE, warning = FALSE}
if(!require(installr))install.packages("installr")
library(installr)

## https://rstudio.github.io/distill/tables.html

# Provides support for HTML tables in Rmarkown
require2(rmarkdown)
require2(kableExtra)

# Contains ggplot2, dpyr, and much more
require2(tidyverse)


require2(Rmisc)
require2(devtools)
require2(xtable)
require2(printr)
require2(stargazer)
require2(DT)
require2(xfun)
require2(psych)
require2(lmtest)
require2(sandwich)
require2(huxtable)
require2(jtools)
require2(tutorial)
require2(car)
require2(olsrr)
require2(broom)
require2(multcomp)
require2(zoo)
require2(sandwich)
require2(dynlm)
require2(orcutt)
require2(pdfetch)
require2(rticles)


# Replaces `paste`
require2(glue)

# Allows animations and intractable HTML plots
require2(plotly)

# Import data from files
require2(readr)
require2(readxl)

# Mange dates
# require2(lubridate)

# Download files
require2(curl)

# Download and import EPI
require2(epidata)

# Adjust currency values for inflation
require2(priceR)
```

### Set up the Knitted table
This will automatically detect if the document is being knited and apply the provided table formatting function or `rmarkdown::paged_table` if not provided.  If `nhead` or `ntail` it will call the `head` or `tail` function respectively and limit the data.  On `0`, it will ignore it.  The default is to create a paginated table on overflow so all the data is accessible but does not take the entire screen.
```{r}
kblstyle=function(data){
	style(kbl(data))
}

innerDisp=function(tbl, style){
	## If the code is kniting
	if(isTRUE(getOption('knitr.in.progress'))){
		return(style(tbl))
	}
	## Otherwise just return the raw tibble to be formatted by RStudio
	return(tbl)
}

disp=function(tbl, nhead=10, ntail=0, style=FALSE, styleHTML=paged_table, stylePDF=kblstyle){
	if(nhead!=0)tbl=head(tbl, n=nhead)
	if(ntail!=0)tbl=tail(tbl, n=ntail)
	if(is.function(style))
		return(innerDisp(tbl, style))
	if(knitr::is_html_output())
	  return(innerDisp(tbl, styleHTML))
	return(innerDisp(tbl, stylePDF))
}
```

```{r eval=FALSE, class.source="bg-info"}
disp(mtcars)
mtcars%>%disp()
# Only output the first 20
mtcars%>%disp(nhead = 20)
# Only output the last 10
mtcars%>%disp(ntail = 10)
# Override to use the standard kbl function
mtcars%>%disp(style = function(t){
	kbl(t)%>%
			style()
})
```

```{r}
ggdisp=function(gg){
	if(
		isTRUE(getOption('knitr.in.progress'))
		&&
		!knitr::is_html_output()
	)	return(gg)
	ggplotly(gg)
}
```

```{r eval=FALSE, class.source="bg-info"}
g=mtcars%>%
	ggplot(aes(mpg, disp))+
	geom_point()
ggdisp(g)
```


```{r echo=F,message=F,warning=F,results='hide'}
# Functions 
predict.prob <- function(lmod,
                      new.data,
                      alpha=0.05,
                      alternative="greater",
                      value)
  {
    prediction <- predict(lmod, 
                          newdata = new.data,
                          interval="predict",
                          level =1-alpha,
                          se.fit = T)
    cv <- qt(p=alpha/2, df = prediction$df, lower.tail = FALSE)
    se <- (prediction$fit[,"upr"] - prediction$fit[,"fit"])/cv
    t.stat <- (value-prediction$fit[,"fit"])/se
    ret = data.frame("value"=value,
                     "prob"=pt(q=t.stat,
                            df=prediction$df,
                            lower.tail = (alternative=="less")),
                     "alternative"=alternative,
                     "fit"=prediction$fit[,"fit"],
                     "upr"=prediction$fit[,"upr"],
                     "lwr"=prediction$fit[,"lwr"],
                     "df" = prediction$df,
                     "cv" = cv,
                     "se" = se,
                     "t.stat" = t.stat
                     )
    return(ret)
  }

predict.plot <- function(prediction){
  x=seq(-4,4,length=400)
  y=dt(x, df=prediction$df)
  t = ifelse((prediction$alternative=="less"),-1,1)  
  x1=seq(t*4,prediction$t.stat,length=400)
  y1=dt(x1, df=prediction$df)
  plot(x,y,type="l", lwd=2, col="black")
  polygon(c(4,prediction$t.stat,x1),c(0,y1,0),col="gray")
  abline(v=0)
}

plot.time <- function (lmod, ln=F) {
  require(ggplot2,dplyr)
  pr <- data.frame(
    Observation = seq(from = 1, to = nrow(lmod$model)),
    Actual = if(ln==T) exp(lmod$model[, 1]) else lmod$model[, 1],
    Fitted = if(ln==T) exp(fitted(lmod)+(summary(lmod)$sigma^2)/2) else fitted(lmod)
  ) %>% pivot_longer(.,
                     cols = 2:ncol(.),
                     names_to = "series",
                     values_to = "values")  %>%
    ggplot(aes(x = Observation, y = values, color = series)) +
    geom_line() +
    ggtitle(lmod$call) +
    theme_classic() +
    scale_color_manual(values = c("#2c7bb6", "#d7191c", "#808080", "#000000")) +
    theme(
      legend.position = "bottom",
      legend.direction = 'horizontal',
      legend.title = element_blank()
    )
  return(pr)
}

plot.fitted <- function(lmod) {
  df = lmod$model
  title = paste("Residuals vs. Fits (Dependent Variable: ",
                names(df)[1],
                ")",
                sep = "")
  pr <- df %>% ggplot(aes(x = fitted(lmod), y = resid(lmod))) +
    geom_ribbon(aes(ymin = -sigma(lmod), ymax = sigma(lmod)),
                fill = "gray",
                alpha = .5) +
    geom_ribbon(aes(ymin = -sigma(lmod) * 2, ymax = sigma(lmod) * 2),
                fill = "lightgray",
                alpha = .5) +
    geom_point() +
    theme_classic() +
    ggtitle(title) +
    ylab("Residules") +
    xlab("Fitted") +
    geom_hline(yintercept = 0,
               linetype = "solid",
               color = "black")
  return(pr)  
}  

plot.normal <- function(lmod) {
  res <- resid(lmod)
  hist(res, probability = T)
  curve(
    dnorm(x, mean = mean(res), sd = (sd(res))),
    col = "darkblue",
    lwd = 2,
    add = TRUE,
    yaxt = "n"
  )
}

```

