---
title: "Wage by Race"
author: "Shawn Graven"
date: "2/12/2021"
output: html_document
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(
	echo = TRUE
)
```

## Import Data
### About the Data
We have two sources of data, one from [BLS](https://www.bls.gov/cps) and the majority of data from [EPI](https://www.epi.org/data/##/?subject=wage-avg&g=*&r=*).

BLS maintains a data set called `cpsaat`, this data summaries the wage earnings per type of job, based on race and gender.  To access the data in R we use a `curl_download` to retrieve the `.xlsx` file off the internet.  To read the file we use the function  `readxl::read_excel`.

EPI hosts a lot of data on wage statistics including, minimum wage, the participation, and earnings of each race, gender, education level, and much more.  Due to the way EPI presents the data, it cannot be downloaded with `curl`.  Instead, I have accessed the data with the package `epidata`, this simple package interfaces with EPI so that you don't have to manually download the data.


### Import cpsaat Data
Make sure we have internet and if not abort if not
```{r check internet}
if(!curl::has_internet())quit()
```

cpsaat data is provided online at <a href="https://www.bls.gov/cps/cpsaat11.xlsx">bls.gov</a>.  As it is a direct link we can download it and save it to a temporary file and process the data with `readxl::read_excel()`
```{r import cpsaat, message=FALSE, warning=FALSE}
## Create a temp file name/location
tmp <- tempfile()
## Download cpsaat data
curl_download("https://www.bls.gov/cps/cpsaat11.xlsx", destfile = tmp)

## Import cpsaat
cpsaat11 <- read_excel(
		tmp,
		col_names = c(
			"Occupation",
			"Total",
			"Women",
			"White",
			"Black/African American",
			"Asian",
			"Hispanic/Latino"
		),
		na = "–",
		col_types = c(
			Occupation="text",
			Total="numeric",
			"Women"="numeric",
			"White"="numeric",
			"Black/African American"="numeric",
			"Asian"="numeric",
			"Hispanic/Latino"="numeric"
		),
		skip = 7
	)%>%
	drop_na(Occupation)
## Remove temp file and var
file.remove(tmp)
rm(tmp)
```

### Import EPI Data
Get the data at <a href="https://www.epi.org/data/##/?subject=wage-avg&g=*&r=*">EPI</a>.  As there is no direct link avalable we cannot use `curl`, instead there is a package that we can use to access the data, `epidata`.  This will download data in the background.
```{r Import EPI Data, message=FALSE, warning=FALSE}
Labor_force_participation <- epidata::get_labor_force_participation_rate(by = "gr")

Medianaverage_hourly_wages <- epidata::get_median_and_mean_wages(by = "gr")

Minimum_wage <- epidata::get_minimum_wage()
```

## Clean Data
As with most data, it will have to be cleaned.  This includes pivoting the tibble into a longer tibble, as it will work better for `ggplot2`.  This current format is called wide format as it has many columns.  To fix this we can convert it into long format, as there are many rows, with `pivot_longer`.  When we do this sometimes the new column we create contains more than one value, to remedy this issue we can use `seperate` and mutate if necessary to get the values in the right column.  Another inconsistancy we should be aware of is that the currency values are in different years, not a large difference, but something that should be corrected.

### Clean cpsaat11

```{r Clean cpsaat11}
cpsaat11%>%disp()

cpsaat11=cpsaat11%>%
	pivot_longer(-c(Occupation, Total), names_to = "Race", values_to = "Percentage")
```

Looks fine.

### Clean Labor_force_participation
```{r Clean Labor_force_participation}
Labor_force_participation%>%disp()

Participation=Labor_force_participation%>%
	pivot_longer(-date, names_to = "Race", values_to = "Participation", values_drop_na = T)%>%
	separate(Race, into = c("Race", "Gender"))

Participation=Participation%>%
	filter(grepl("women|men", Race, ignore.case = T))%>%
	mutate(
		Gender=Race,
		Race=NA_character_
	)%>%
	union(
		Participation%>%
			filter(!grepl("women|men", Race, ignore.case = T))
	)
Participation%>%
	filter(!is.na(Race))
rm(Labor_force_participation)
```



### Clean Medianaverage_hourly_wages
```{r Clean Medianaverage_hourly_wages}
Medianaverage_hourly_wages%>%disp()
Wages=Medianaverage_hourly_wages%>%
	pivot_longer(-date, names_to = "Race", values_to = "Wage", values_drop_na = T)%>%
	separate(Race, into = c("Race", "Gender", "Summary"), fill = "left")

## Race is in the wrong location sometimes
Wages=Wages%>%
	filter(!grepl("women|men", Gender, ignore.case = T))%>%
	mutate(
		Race=Gender,
		Gender=NA_character_
	)%>%
	union(
		Wages%>%
			filter(grepl("women|men", Gender, ignore.case = T))
	)
## No need to keep the Average and Median split up
Wages=Wages%>%
	pivot_wider(names_from = Summary, values_from = Wage)
rm(Medianaverage_hourly_wages)
```

### Clean Minimum_wage
This data has data in terms of 2018, the other data is in 2019 USD.  Although small, there will be a difference and we need to adjust for inflation.  The package `priceR` allows us to convert those monitary values into other ones using online inflation data.
```{r Clean Minimum_wage}
Minimum_wage%>%disp()
##adjust for inflation to get to common 2019
Minimum_wage=Minimum_wage%>%
	mutate(
		Min2019=priceR::adjust_for_inflation(
			federal_minimum_wage_real_x_2018_dollars,
			2018,
			"US",
			2019
		)
	)

Minimum_wage=Minimum_wage%>%
	rename(MinCur=federal_minimum_wage_nominal_dollars)%>%
	select(Min2019, MinCur, date)
```


### Fix inconsistant case
As the data was imported with `epidata`, the colum names have been changed from what the csv has.  So we need to fix that to conform to consistancy.
```{r Fix Case}
Wages=Wages%>%
	rename(
		Date=date,
		Median=median,
		Average=average
	)

Participation=Participation%>%
	rename(Date=date)

Minimum_wage=Minimum_wage%>%
	rename(Date=date)
```
