---
title: "Wage by Race"
author: "Shawn Graven"
date: "2/12/2021"
output: html_document
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(
	echo = TRUE
)
```

## Setup
### Install and Attach
`installr` provides `require2`, this will install a package if it is missing and library it.  Unfortunetly, `intall` is a package too, so you cannot use `require2` on it.
```{r, message = FALSE, warning = FALSE}
if(!require(installr))install.packages("installr")
library(installr)

## https://rstudio.github.io/distill/tables.html

require2(rmarkdown)
require2(kableExtra)
require2(tidyverse)
require2(glue)
require2(readr)
require2(plotly)
require2(readr)
require2(readxl)
require2(lubridate)
require2(curl)
require2(epidata)
```

### Set up the Knitted table
This will automaticaly detect if the document is being knited and apply the provided table formatting function or `rmarkdown::paged_table` if not provided.  If `nhead` or `ntail` it will call the `head` or `tail` function respectively and limit the data.  On `0`, it will ignore it.  The default is to create a paginated table on overflow so all the data is accessable but does not take the entire screen.
```{r}
disp=function(tbl, nhead=0, ntail=0, style=paged_table){
	if(!is.function(style))style=function(t){
		kbl(t)%>%
			style()%>%
			return()
	}
	## If the code is kniting
	if(isTRUE(getOption('knitr.in.progress'))){
		if(nhead!=0)tbl=head(tbl, n=nhead)
		if(ntail!=0)tbl=tail(tbl, n=ntail)
		return(
			tbl%>%
  		style()
		)
	}
	## Otherwise just return the raw tible to be formated by RStudio
	return(tbl)
}
```

```{r eval=FALSE, class.source="bg-info"}
mtcars%>%disp()
mtcars%>%disp(nhead = 20)
mtcars%>%disp(ntail = 10)
mtcars%>%disp(style = function(t){
	kbl(t)%>%
			style()%>%
			return()
})
```

## Import Data
Make sure we have internet and if not abort if not
```{r check internet}
if(!curl::has_internet())quit()
```

### Import cpsaat Data
cpsaat data is provided online at <a href="https://www.bls.gov/cps/cpsaat11.xlsx">bls.gov</a>.  As it is a direct link we can donload it and save it to a temporary file and process the data with `readxl::read_excel()`
```{r import cpsaat, message=FALSE, warning=FALSE}
## Create a temp file name/location
tmp <- tempfile()
## Download cpsaat data
curl_download("https://www.bls.gov/cps/cpsaat11.xlsx", destfile = tmp)

## Import cpsaat
cpsaat11 <- read_excel(
		tmp,
		col_names = c(
			"Occupation",
			"Total",
			"Women",
			"White",
			"Black/African American",
			"Asian",
			"Hispanic/Latino"
		),
		na = "–",
		col_types = c(
			Occupation="text",
			Total="numeric",
			"Women"="numeric",
			"White"="numeric",
			"Black/African American"="numeric",
			"Asian"="numeric",
			"Hispanic/Latino"="numeric"
		),
		skip = 7
	)%>%
	drop_na(Occupation)
## Remove temp file and var
file.remove(tmp)
rm(tmp)
```

### Import EPI Data
Get the data at <a href="https://www.epi.org/data/##/?subject=wage-avg&g=*&r=*">EPI</a>.  As there is no direct link avalable we cannot use `curl`, instead there is a package that we can use to access the data, `epidata`.  This will download data in the background.
```{r Import EPI Data, message=FALSE, warning=FALSE}
Labor_force_participation <- epidata::get_labor_force_participation_rate(by = "gr")

Medianaverage_hourly_wages <- epidata::get_median_and_mean_wages(by = "gr")

Minimum_wage <- epidata::get_minimum_wage()
```

## Clean Data
The data is in a terrible format for use in `ggplot2`, and we call this wide format as it has many columns.  To fix this we can convert it into long format, as there are many rows, with `pivot_longer`.

### Clean cpsaat11

```{r Clean cpsaat11}
cpsaat11%>%disp()

cpsaat11=cpsaat11%>%
	pivot_longer(-c(Occupation, Total), names_to = "Race", values_to = "Percentage")
```

Looks fine.

### Clean Labor_force_participation
```{r Clean Labor_force_participation}
Labor_force_participation%>%disp()

Participation=Labor_force_participation%>%
	pivot_longer(-date, names_to = "Race", values_to = "Participation", values_drop_na = T)%>%
	separate(Race, into = c("Race", "Gender"))

Participation=Participation%>%
	filter(grepl("women|men", Race, ignore.case = T))%>%
	mutate(
		Gender=Race,
		Race=NA_character_
	)%>%
	union(
		Participation%>%
			filter(!grepl("women|men", Race, ignore.case = T))
	)
Participation%>%
	filter(!is.na(Race))
rm(Labor_force_participation)
```



### Clean Medianaverage_hourly_wages
```{r Clean Medianaverage_hourly_wages}
Medianaverage_hourly_wages%>%disp()
Wages=Medianaverage_hourly_wages%>%
	pivot_longer(-date, names_to = "Race", values_to = "Wage", values_drop_na = T)%>%
	separate(Race, into = c("Race", "Gender", "Summary"), fill = "left")

## Race is in the wrong location sometimes
Wages=Wages%>%
	filter(!grepl("women|men", Gender, ignore.case = T))%>%
	mutate(
		Race=Gender,
		Gender=NA_character_
	)%>%
	union(
		Wages%>%
			filter(grepl("women|men", Gender, ignore.case = T))
	)
## No need to keep the Average and Median split up
Wages=Wages%>%
	pivot_wider(names_from = Summary, values_from = Wage)
rm(Medianaverage_hourly_wages)
```

### Clean Minimum_wage
This data has data in terms of 2018, the other data is in 2019 USD.  Although small, there will be a difference and we need to adjust for inflation.  The package `priceR` allows us to convert those monitary values into other ones using online inflation data.
```{r Clean Minimum_wage}
Minimum_wage%>%disp()
##adjust for inflation to get to common 2019
Minimum_wage=Minimum_wage%>%
	mutate(
		Min2019=priceR::adjust_for_inflation(
			federal_minimum_wage_real_x_2018_dollars,
			2018,
			"US",
			2019
		)
	)

Minimum_wage=Minimum_wage%>%
	rename(MinCur=federal_minimum_wage_nominal_dollars)%>%
	select(Min2019, MinCur, date)
```


### Fix inconsistant case
As the data was imported with `epidata`, the colum names have been changed from what the csv has.  So we need to fix that to conform to consistancy.
```{r Fix Case}
Wages=Wages%>%
	rename(
		Date=date,
		Median=median,
		Average=average
	)

Participation=Participation%>%
	rename(Date=date)

Minimum_wage=Minimum_wage%>%
	rename(Date=date)
```

## Graph
### Average and Medium Wage over Time by Race and Gender
```{r}
g=Wages%>%
	ggplot(aes(col=Race, x=Date))+
	geom_line(aes(y=Average))+
	geom_line(aes(y=Min2019, col=NULL), data=Minimum_wage, size=2)+
	facet_wrap(~Gender)
ggplotly(g)

g=Wages%>%
	ggplot(aes(col=Race, x=Date))+
	geom_line(aes(y=Median))+
	geom_line(aes(y=Min2019, col=NULL), data=Minimum_wage, size=2)+
	facet_wrap(~Gender)
ggplotly(g)
```

### Scatter Plot over Time
```{r}
g=Wages%>%
	ggplot()+
	geom_point(aes(x=Median, y=Average, col=Race, shape=Gender, frame=Date))+
	ggtitle("Median vs Average Wage per Race and Gender over Time")
ggplotly(g)
```
