---
title: "Graph"
author: "Shawn Graven"
date: "2/18/2021"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Wages according to Jobs
### Sumarise data according to income of jobs
This data is currently unusable as there is only one opservation per type of job, we don't have over time statistics.  We do however, have a snapshot of the diverse earnings, we don't care what the job is, but the average wage of each race per earning bracket.
```{r}
cpsaat11%>%
	ggplot(aes(x=log(Total)))+
	geom_boxplot()

# Generate the percentiles
se=quantile(log(cpsaat11$Total), seq(0, 1, by=.1), na.rm=T)

# Add outlyers
se["200%"]=Inf

# break into groups and drop NAs
d=cpsaat11%>%
	drop_na(Percentage)%>%
	group_by(gr=cut(Total, breaks=exp(se)), Race)

# Summarize the data and remove women as it is not a race
# This is so it add up to 100% or so
d=d%>%
	summarise(Percentage=mean(Percentage), Total=mean(Total))%>%
	filter(Race!="Women")
d
```

### Is there missing data
```{r}
cpsaat11%>%
	drop_na(Percentage)%>%
	filter(Total<30)
```
No, we just have a lack of observations for poor paying jobs.


### Graph
```{r}
g=d%>%
	ggplot(aes(fill=Race, y=Percentage, x=gr))+
	geom_col()+
	xlab("Wage Bracket")+
	ylab("Percentage of Earnings")+
	ggtitle("Percentage of Earnings per Wage Braket and Race")
ggplotly(g)

g=d%>%
	ggplot(aes(fill=Race, y=Percentage*Total, x=gr))+
	geom_col(position = "dodge2")+
	scale_y_log10()+
	xlab("Wage Bracket")+
	ylab("Earnings in USD")+
	ggtitle("Total Earnings per Wage Braket and Race")
ggplotly(g)

g=d%>%
	ggplot(aes(fill=gr, x=1, y=Percentage))+
	geom_col(position = "dodge2")+
	facet_wrap(~Race)+
	xlab("Wage Bracket")+
	ylab("Percentage of Earnings")+
	ggtitle("Percentage of Earnings per Wage Braket and Race")
ggplotly(g)


g=d%>%
	ggplot(aes(fill=gr, x=1, y=Percentage*Total))+
	geom_col(position = "dodge2")+
	facet_wrap(~Race)+
	scale_y_log10()+
	xlab("Wage Bracket")+
	ylab("Earnings in USD")+
	ggtitle("Log of Total Earnings per Wage Braket and Race")
ggplotly(g)


g=d%>%
	ggplot(aes(fill=Race, x=1, y=Percentage*Total))+
	geom_col(position = "dodge2")+
	facet_wrap(~gr)+
	xlab("Wage Bracket")+
	ylab("Earnings in USD")+
	ggtitle("Total Earnings per Wage Braket and Race")
ggplotly(g)
```